Persistence of marine populations under climate and fishing

### 2014-06-11 Writing/Appendix.tex
adding recursive eq biomass equations to appendix

@@

\subsection{Approximate critical harvesting proportions \label{approxcrit}}
~\\We will use the following Taylor series to make approximations of the critical harvesting proportions under the two dispersal kernels:
\begin{align*}
\cos(x)&=1-\frac{x^2}{2}
\\ \cos^2(x)&=1-x^2
\\ \sin^2(x)&=x^2-\frac{x^4}{3}
\\ erf(x)&=\frac{2}{\sqrt{\pi}}(x-\frac{x^3}{3})
\\ \exp(x)&=1+x+\frac{x^2}{2}
\end{align*}
For the Gaussian kernel we found 
\begin{equation}
h^*=1-\frac{2\sqrt{2}\exp\left(\frac{c^{2}}{8D}\right)}{R_0\left[erf\left(\frac{L-c}{2\sqrt{2D}}\right)-erf\left(\frac{-L-c}{2\sqrt{2D}}\right)\right]}
\end{equation} 
Using the Taylor series and the fact that $D=\frac{\sigma^2}{2}$ where $\sigma^2$ is the variance of the exponential kernel,
\begin{align*}
h^*&\sim 1-\frac{\sqrt{2\pi}(1+\frac{c^2}{8D}+\frac{c^4}{128D^2})}{R_0\sqrt{\pi}\left[\frac{L-c}{2\sqrt{2D}}-\frac{(L-c)^3}{3(2\sqrt{2D})^3}-\frac{-L-c}{2\sqrt{2D}}+\frac{(-L-c)^3}{3(2\sqrt{2D})^3)}\right]}
%\\&= 1-\frac{\sqrt{2\pi}(1+\frac{c^2}{8D}+\frac{c^4}{128D^2})}{R_0\left[\frac{2L}{2\sqrt{2D}}+\frac{-L^3+3L^2c-3Lc^2+c^3-L^3-3L^2c-3Lc^2-c^3}{3(2\sqrt{2D})^3}\right]}
%\\&= 1-\frac{\sqrt{2\pi}(1+\frac{c^2}{8D}+\frac{c^4}{128D^2})}{R_0\left[\frac{L}{\sqrt{2D}}-2\frac{L^3+3Lc^2}{3(2\sqrt{2D})^3}\right]}
%\\&= 1-\frac{\sqrt{2\pi}(1+\frac{c^2}{8D}+\frac{c^4}{128D^2})}{R_0L\left[\frac{48D-2(L^2+3c^2)}{3(2\sqrt{2D})^3}\right]}
%\\&= 1-\frac{3*32D\sqrt{D\pi}(1+\frac{c^2}{8D}+\frac{c^4}{128D^2})}{R_0L\left(48D-2(L^2+3c^2)\right)}
%\\&= 1-\frac{3*32D\sqrt{D\pi}(\frac{128D^2+16c^2D+c^4}{128D^2})}{R_0L\left(48D-2(L^2+3c^2)\right)}
%\\&= 1-\frac{3\sqrt{\pi}(128D^2+16c^2D+c^4)}{4R_0L\sqrt{D}\left(48D-2(L^2+3c^2)\right)}
%\\&= 1-\frac{3\sqrt{2\pi}(32\sigma^4+8c^2\sigma^2+c^4)}{4R_0L\sigma\left(24\sigma^2-2(L^2+3c^2)\right)}
\\&= 1-\frac{1}{R_0}\cdot\frac{3\sqrt{2\pi}}{8L}\frac{(32\sigma^4+8c^2\sigma^2+c^4)}{\sigma\left(12\sigma^2-(L^2+3c^2)\right)}
\end{align*}
For the sinusoidal kernel we found 
\begin{equation}
h^*=1-\frac{1}{R_0}\cdot\frac{4wL}{w^2L^2-\sin^2(wL)}\left[\cos(wc)-\sqrt{\cos^2(wc)-1+\frac{\sin^2(wL)}{w^2L^2}}\right] 
\end{equation} 
Using the Taylor series and the fact that $w=\frac{\sqrt{\frac{\pi^2}{4}-2}}{\sigma}$ where $\sigma^2$ is the variance of the sinusoidal kernel,
\begin{align*}
h^*&\sim 1-\frac{1}{R_0}\cdot\frac{12wL}{w^4L^4}\left[1-\frac{w^2c^2}{2}-\sqrt{1-w^2c^2-\frac{w^2L^2}{3}}\right]
%\\&=1-\frac{1}{R_0}\cdot\frac{12}{w^3L^3}\left[1-\frac{w^2c^2}{2}-\sqrt{1-w^2c^2-\frac{w^2L^2}{3}}\right]
%\\&=1-\frac{1}{R_0}\cdot\frac{12\sigma^3}{L^3(\frac{\pi^2}{4}-2)^{3/2}}\left[1-\frac{(\frac{\pi^2}{4}-2)c^2}{2\sigma^2}-\sqrt{1-\frac{(\frac{\pi^2}{4}-2)c^2}{\sigma^2}-\frac{(\frac{\pi^2}{4}-2)L^2}{3\sigma^2}}\right]
%\\&=1-\frac{1}{R_0}\cdot\frac{6\sigma}{L^3(\frac{\pi^2}{4}-2)^{3/2}}\left[2\sigma^2-(\frac{\pi^2}{4}-2)c^2-\frac{2}{\sqrt{3}}\sigma\sqrt{3\sigma^2-(\frac{\pi^2}{4}-2)3c^2-(\frac{\pi^2}{4}-2)L^2}\right]
%\\&=1-\frac{1}{R_0}\cdot\frac{6\sigma}{L^34(\frac{\pi^2}{4}-2)^{3/2}}\left[8\sigma^2-(\pi^2-8)c^2-\frac{4}{\sqrt{3}}\sigma\sqrt{12\sigma^2-(\pi^2-8)3c^2-(\pi^2-8)L^2}\right]
%\\&=1-\frac{12}{R_0L^3(\pi^2-8)^{3/2}}\cdot\sigma\left[8\sigma^2-(\pi^2-8)c^2-\frac{4}{\sqrt{3}}\sigma\sqrt{12\sigma^2-(\pi^2-8)3c^2-(\pi^2-8)L^2}\right]
\\&=1-\frac{1}{R_0}\cdot\frac{4\sqrt{3}}{L^3(\pi^2-8)^{3/2}}\cdot\sigma\left[8\sqrt{3}\sigma^2-(\pi^2-8)\sqrt{3}c^2-4\sigma\sqrt{12\sigma^2-(\pi^2-8)(3c^2+L^2)}\right]
\end{align*}
In the case of both kernels, the critical harvesting proportion can be approximated by a function that looks like 
\begin{equation}
h^*\sim1- \frac{1}{R_0}\cdot g(L)q(\sigma^2,c^2,L^2+3c^2)
\end{equation}
where $g(L)$ is a decreasing function of the length of the viable patch $L$.

>>>>

To find the equilibrium biomass, we rewrite (\ref{pulse}) using the separable kernel as in \cite{Latore:1998fk}:

\begin{align*}
 n^*(x)&=\int_{-L/2}^{L/2}k(x+c-y)R_0g(f(n^*(y)))dy
 \\&= \int_{-L/2}^{L/2}\left(\sum_{n=1}^\infty a_n(x)b_n(y-c)\right)R_0g(f(n^*(y)))dy
  \\&=\sum_{n=1}^\infty a_n(x) \int_{-L/2}^{L/2}b_n(y-c)R_0g(f(n^*(y)))dy
\end{align*}
If we define $m_n=\int_{-L/2}^{L/2}b_n(y-c)R_0g(f(n^*(y)))dy$ then we find that 
\begin{align}
n^*(x)&=\sum_{n=1}^\infty m_na_n(x) \text { and } \notag
\\m_n&=\int_{-L/2}^{L/2}b_n(y-c)R_0g\left(f\left(\sum_{n=1}^\infty m_na_n(y)\right)\right)dy \label{recursive}
\end{align}
The recursive equation (\ref{recursive}) allows us to find the $m_n$ numerically and we then find the total equilibrium biomass by integrating $n^*(x)$ over space.

@@

\subsection{Approximate critical harvesting proportions \label{approxcrit}}
~\\We will use the following Taylor series to make approximations of the critical harvesting proportions under the two dispersal kernels:
\begin{align*}
\cos(x)&=1-\frac{x^2}{2}
\\ \cos^2(x)&=1-x^2
\\ \sin^2(x)&=x^2-\frac{x^4}{3}
\\ erf(x)&=\frac{2}{\sqrt{\pi}}(x-\frac{x^3}{3})
\\ \exp(x)&=1+x+\frac{x^2}{2}
\end{align*}
For the Gaussian kernel we found 
\begin{equation}
h^*=1-\frac{2\sqrt{2}\exp\left(\frac{c^{2}}{8D}\right)}{R_0\left[erf\left(\frac{L-c}{2\sqrt{2D}}\right)-erf\left(\frac{-L-c}{2\sqrt{2D}}\right)\right]}
\end{equation} 
Using the Taylor series and the fact that $D=\frac{\sigma^2}{2}$ where $\sigma^2$ is the variance of the exponential kernel,
\begin{align*}
h^*&\sim 1-\frac{\sqrt{2\pi}(1+\frac{c^2}{8D}+\frac{c^4}{128D^2})}{R_0\sqrt{\pi}\left[\frac{L-c}{2\sqrt{2D}}-\frac{(L-c)^3}{3(2\sqrt{2D})^3}-\frac{-L-c}{2\sqrt{2D}}+\frac{(-L-c)^3}{3(2\sqrt{2D})^3)}\right]}
%\\&= 1-\frac{\sqrt{2\pi}(1+\frac{c^2}{8D}+\frac{c^4}{128D^2})}{R_0\left[\frac{2L}{2\sqrt{2D}}+\frac{-L^3+3L^2c-3Lc^2+c^3-L^3-3L^2c-3Lc^2-c^3}{3(2\sqrt{2D})^3}\right]}
%\\&= 1-\frac{\sqrt{2\pi}(1+\frac{c^2}{8D}+\frac{c^4}{128D^2})}{R_0\left[\frac{L}{\sqrt{2D}}-2\frac{L^3+3Lc^2}{3(2\sqrt{2D})^3}\right]}
%\\&= 1-\frac{\sqrt{2\pi}(1+\frac{c^2}{8D}+\frac{c^4}{128D^2})}{R_0L\left[\frac{48D-2(L^2+3c^2)}{3(2\sqrt{2D})^3}\right]}
%\\&= 1-\frac{3*32D\sqrt{D\pi}(1+\frac{c^2}{8D}+\frac{c^4}{128D^2})}{R_0L\left(48D-2(L^2+3c^2)\right)}
%\\&= 1-\frac{3*32D\sqrt{D\pi}(\frac{128D^2+16c^2D+c^4}{128D^2})}{R_0L\left(48D-2(L^2+3c^2)\right)}
%\\&= 1-\frac{3\sqrt{\pi}(128D^2+16c^2D+c^4)}{4R_0L\sqrt{D}\left(48D-2(L^2+3c^2)\right)}
%\\&= 1-\frac{3\sqrt{2\pi}(32\sigma^4+8c^2\sigma^2+c^4)}{4R_0L\sigma\left(24\sigma^2-2(L^2+3c^2)\right)}
\\&= 1-\frac{1}{R_0}\cdot\frac{3\sqrt{2\pi}}{8L}\frac{(32\sigma^4+8c^2\sigma^2+c^4)}{\sigma\left(12\sigma^2-(L^2+3c^2)\right)}
\end{align*}
For the sinusoidal kernel we found 
\begin{equation}
h^*=1-\frac{1}{R_0}\cdot\frac{4wL}{w^2L^2-\sin^2(wL)}\left[\cos(wc)-\sqrt{\cos^2(wc)-1+\frac{\sin^2(wL)}{w^2L^2}}\right] 
\end{equation} 
Using the Taylor series and the fact that $w=\frac{\sqrt{\frac{\pi^2}{4}-2}}{\sigma}$ where $\sigma^2$ is the variance of the sinusoidal kernel,
\begin{align*}
h^*&\sim 1-\frac{1}{R_0}\cdot\frac{12wL}{w^4L^4}\left[1-\frac{w^2c^2}{2}-\sqrt{1-w^2c^2-\frac{w^2L^2}{3}}\right]
%\\&=1-\frac{1}{R_0}\cdot\frac{12}{w^3L^3}\left[1-\frac{w^2c^2}{2}-\sqrt{1-w^2c^2-\frac{w^2L^2}{3}}\right]
%\\&=1-\frac{1}{R_0}\cdot\frac{12\sigma^3}{L^3(\frac{\pi^2}{4}-2)^{3/2}}\left[1-\frac{(\frac{\pi^2}{4}-2)c^2}{2\sigma^2}-\sqrt{1-\frac{(\frac{\pi^2}{4}-2)c^2}{\sigma^2}-\frac{(\frac{\pi^2}{4}-2)L^2}{3\sigma^2}}\right]
%\\&=1-\frac{1}{R_0}\cdot\frac{6\sigma}{L^3(\frac{\pi^2}{4}-2)^{3/2}}\left[2\sigma^2-(\frac{\pi^2}{4}-2)c^2-\frac{2}{\sqrt{3}}\sigma\sqrt{3\sigma^2-(\frac{\pi^2}{4}-2)3c^2-(\frac{\pi^2}{4}-2)L^2}\right]
%\\&=1-\frac{1}{R_0}\cdot\frac{6\sigma}{L^34(\frac{\pi^2}{4}-2)^{3/2}}\left[8\sigma^2-(\pi^2-8)c^2-\frac{4}{\sqrt{3}}\sigma\sqrt{12\sigma^2-(\pi^2-8)3c^2-(\pi^2-8)L^2}\right]
%\\&=1-\frac{12}{R_0L^3(\pi^2-8)^{3/2}}\cdot\sigma\left[8\sigma^2-(\pi^2-8)c^2-\frac{4}{\sqrt{3}}\sigma\sqrt{12\sigma^2-(\pi^2-8)3c^2-(\pi^2-8)L^2}\right]
\\&=1-\frac{1}{R_0}\cdot\frac{4\sqrt{3}}{L^3(\pi^2-8)^{3/2}}\cdot\sigma\left[8\sqrt{3}\sigma^2-(\pi^2-8)\sqrt{3}c^2-4\sigma\sqrt{12\sigma^2-(\pi^2-8)(3c^2+L^2)}\right]
\end{align*}
In the case of both kernels, the critical harvesting proportion can be approximated by a function that looks like 
\begin{equation}
h^*\sim1- \frac{1}{R_0}\cdot p(L)q(\sigma^2,c^2,L^2+3c^2)
\end{equation}
where $p(L)$ is a decreasing function of the length of the viable patch $L$.
